A reproducible framework for undergraduate data science research

### 2019-12-06 Rmd/discussion.Rmd
expanded discussion

>>>>

## Integrating more mentoring activities

Our framework would benefit students more if we explicitly incorporate more 
mentoring activities. Through professional development courses at the University
of Wisconsin-Madison's Delta Program, we received training in how to offer 
professional support to students. While we both informally supported our
students, the Delta Program suggested
ways to encourage the student's professional development through structured
conversations and goal-setting. Additions like this would only enhance our 
framework.

@baker2010beyond discuss the role of faculty "developers" in 
student success. A faculty "developer", as envisioned by @higgins2001reconceptualizing, 
offers not only psychosocial and career support, like a mentor, but also 
supports students' academic goals. Such relationships between developers 
and students benefit both parties. The student gets support while the 
developer refines her teaching and expands her scholarly network. We anticipate
expanding our framework to more holistically support students.

### 2019-12-06 Rmd/methods.Rmd
expanded discussion

@@

In the case of the event detection project, we e

@@

Students wrote R code to parse and organize tweet JSON []. They organized their R code into a package, and shared it on Github (https://github.com/rturn/parseTweetFiles). 
Each tweet's JSON included required fields, and, possibly, some optional fields.

@@

Both mentored students combined computing with data analysis in 
the practice of statistics. 
They used a combination of latent dirichlet allocation topic 
modeling, sentiment analysis, and time series analysis to reach 
conclusions about real world data.

@@

The second student project involved latent Dirichlet allocation modeling of
tweet words at distinct time points to detect social media events [@blei2003latent]. 
Latent Dirichlet allocation is a bayesian nonparametric method for modeling text corpora as the result 
of words chosen from topics.

@@

>>>>

We encouraged students to complement tweets with additional data from publicly 
available sources.

@@

In the case of the event detection project, our student created 
word clouds for every inferred "topic". 
He also presented most probable words from each inferred topic, i.e., each distribution over words, as a bar plot.

The student working on sentiment analysis and market index prices plotted a 
daily sentiment "score" over time and presented it beside a plot of daily market 
index prices and compared the two plots.

@@

Students wrote R code to parse and organize tweet JSON. 
They organized their R code into a package, and shared it on Github (https://github.com/rturn/parseTweetFiles). 
Each tweet's JSON included required fields, and, possibly, some optional fields. 
Thus, students' code needed to accommodate variability in tweet structure.

@@

Both mentored students combined computing with data analysis in 
the practice of statistics. 
They used a combination of latent dirichlet allocation topic 
modeling, sentiment analysis, and time series analysis to reach 
conclusions about real world phenomena.

@@

The second student project involved latent Dirichlet allocation modeling of
tweet words at distinct time points to detect social media events [@blei2003latent]. 
Latent Dirichlet allocation is a bayesian nonparametric method for modeling text corpora as the result 
of words chosen from topics. The student treated tweets as "documents" (in the parlance of 
topic modeling). The goal of topic modeling, then, was to infer the underlying "topics" (or probability distributions over words) from a collection of tweets.

@@

As we stated above, the students created an R package, `parseTweetFiles`, version controlled it with `git`, and shared it via Github.
